A universal standard archive file for adsorption data

### 2020-11-30 manuscript/article.tex
drafting missing summary

To illustrate the importance of a universal data format for adsorption data we can compare data contained within an AIF to data digitized from a figure in a manuscript, for the same experiment.
The porous material DUT-6 (also referred to as MOF-206) is a metal-organic framework produced from zinc nitrate and two different different ligands; 2,6-naphthalenedicarboxylic acid and benzene-1,3,5-tribenzoic acid.\cite{10.1002/anie.200904599}
DUT-6 has mesopores with dodecahedral geometry and smaller cages that produce an extremely porous material with large adsorption capacities for\textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
The nitrogen adsorption isotherm at 77~K was reported in the original manuscript using relative pressure and a linear axis (Figure~/ref{fgr:example}).
From this plot the isotherm can be classified  as  type  Ib clearly exhibiting characteristics of a hierarchal pore system with micropore and mesopores.
Clearly there is a distinct step $p/p_0$ = 0.17, however, from this plot it is not possible to correctly identify low pressure features.
The low pressure regions is important for understanding the process of initial pore filling or for independent application of analysis methods, such as the Brunauer–Emmett–Teller (BET) method.
The reported isotherm was digitized using WebPlotDigitizer, which uses a time-consuming but powerful point-picking methodology.\cite{webplotdigitizer}
In this methodology each point in the graph is identified by clicking on the image area and the point's location in on-screen pixels is then converted to data valued based on an axes calibration.
The digitized isotherm and the data from the experiment, when plotted on semi-log axes, clearly shows important low pressure information is lost when this information is simply included as a figure in a manuscript (Figure~\ref{fgr:example}).

To prevent this information loss and to allow further analysis of reported adsorption experiments by other researchers adsorption data should be archived and shared using the a universal and complete data format like that of the AIF.

>>>>

To illustrate the importance of a universal data format for adsorption data we can compare data contained within an AIF to data digitized from a figure in a manuscript, for the same experiment.
The porous material DUT-6 (also referred to as MOF-206) is a metal-organic framework produced from zinc nitrate and two different different ligands; 2,6-naphthalenedicarboxylic acid and benzene-1,3,5-tribenzoic acid.\cite{10.1002/anie.200904599}
DUT-6 has mesopores with dodecahedral geometry and smaller cages that produce an extremely porous material with large adsorption capacities for\textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
The nitrogen adsorption isotherm at 77~K was reported in the original manuscript using relative pressure and a linear axis (Figure~/ref{fgr:example}).
From this plot the isotherm can be classified  as  type  Ib, clearly exhibiting characteristics of a hierarchal pore system with micropores and mesopores.
There is evidently a distinct step $p/p_0$ = 0.17, however, from this plot it is not possible to correctly identify low pressure features.
The low pressure regions is important for understanding the process of initial pore filling or for independent application of analysis methods, such as the Brunauer–Emmett–Teller (BET) method.\cite{10.1016/S0167-2991(07)80008-5}
The reported isotherm was digitized using WebPlotDigitizer, which uses a time-consuming but powerful point-picking methodology.\cite{webplotdigitizer}
In this methodology, each point in the graph is identified by clicking on the image area and the point's location in on-screen pixels is then converted to data values, based on an axes calibration.
The digitized isotherm and the data from the experiment, when plotted on semi-log axes, clearly shows important low pressure information, such as the point of initial pore-filling, is lost when this information is simply included as a figure in a manuscript (Figure~\ref{fgr:example}).

To prevent this information loss and to allow further analysis of reported adsorption experiments by other researchers, adsorption data should be archived and shared using a universal and complete data format like that of the AIF.
